A systematic search for transiting planets using \KT

### 2015-02-11 ms.tex
more words about FPs

To measure \emph{centroid offsets}, we start by empirically measuring the
pixel centroid time series for each candidate by modeling the pixels near the
peak as a two-dimensional quadratic and finding the maximum at each time.
This method has been shown to produce higher precision centroid measurements
than center-of-light estimates (@HOGG: is this true? Is there a citation? MJ
in prep?).
Figure SOMEFIGURE shows the measure $x$ and $y$ pixel coordinate traces for
SOMECANDIDATE.
Much like the photometry, this signal is dominated by the rigid body motion
of the spacecraft and we can, in fact, model it identically.
Previously (SOMEEQUATION), we modeled the light curve as a linear combination
of ELCs and a simple box transit model at a given period, phase, and duration.
Under this model, the maximum likelihood depth can be computed analytically.
If we apply \emph{exactly the same model} to the centroid trace, the ``depth''
that we compute becomes the centroid motion in transit in units of pixels.

In that data, centroid positions are measured for the data during and out of
transit by coadding all the relevant frames in each quarter.
Such a technique is feasible due to the remarkably stable pointing of the
instrument.
Searching for centroid variations with this method is more difficult in \KT:
to measure a centroid offset, one must know where the centroid is
supposed to be.
With \KT\ this is only possible if one understands the pointing of the
spacecraft at a specific time.
In theory, this is possible: the spacecraft is a rigid body, and by measuring
the mean motion of stars across the detector over time, the
Euler angles can be inferred at all times.
However, properly measuring positions of stars is a difficult problem:
the centroid depends sensitively on the (unknown) flat field, which must
be simultaneously inferred.

While the traditional method to measure centroids is significantly more
challenging with \KT\ data, we have developed an alternative method
to identify centroid offsets during transits in our data.
In our data analysis, we model the systematics in the light curve
caused by spacecraft motion, constrained by the ensemble of all stars in
the field of view.
The same can be done with the positions of each star, instead of the flux,
as a function of time.
In this case, for each candidate, we model the time series of centroid
positions in each dimension as a linear combination of our PCA basis vectors
plus a shift of unknown amplitude during transit events.
Such a technique enables us to measure the centroid shift during transit and
quantify an uncertainty of the size of this shift.

%Therefore, false positives caused by background eclipsing binaries which could
%be identified as such by \kepler\ data alone will be much more difficult to
%distinguish in \KT\ data, making high-contrast adaptive optics images of
%planet candidates an essential follow-up tool.

>>>>

To measure \emph{centroid offsets}, we start by empirically measuring the
pixel centroid time series for each candidate by modeling the pixels near the
peak as a two-dimensional quadratic and finding the maximum at each time.
This method has been shown to produce higher precision centroid measurements
than center-of-light estimates (@HOGG: is this true? Is there a citation? MJ
in prep?).
Figure SOMEFIGURE shows the measure $x$ and $y$ pixel coordinate traces for
SOMECANDIDATE.
Much like the photometry, this signal is dominated by the rigid body motion
of the spacecraft and we can, in fact, model it identically.
Previously (SOMEEQUATION), we modeled the light curve as a linear combination
of ELCs and a simple box transit model at a given period, phase, and duration.
Under this model, the maximum likelihood depth can be computed analytically.
If we apply \emph{exactly the same model} to the centroid trace, the ``depth''
that we compute becomes the centroid motion in transit in units of pixels.
Since the motions won't necessarily point in a consistent direction across
transits, we treat each transit independently and report the average offset
amplitude weighted by the precision of each measurement.
To compute the significance of a centroid offset, we bootstrap the offset
amplitude for models at the same period and duration but randomly oriented
phases.
If the centroid measured for the candidate transit is substantially larger
(by SOMEAMOUNT) than the random realizations, then the candidate is labeled
as a false positive.
Figure SOMEFIGURE shows the distribution of centroid offsets across our
catalog and YYYY---or ZZZZ\%---of our candidates fail this test.

We also test the consistency \emph{between even and odd transit depths} for
each of our candidates.
As described in SOMESECTION, our method for transit search automatically
rejects signals with wildly varying depths but.

Blah blah blah.
Therefore, false positives caused by background eclipsing binaries which could
be identified as such by \kepler\ data alone will be much more difficult to
distinguish in \KT\ data, making high-contrast adaptive optics images of
planet candidates an essential follow-up tool.
